Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals

### 2021-11-18 09_Article/01_Revision2_Reviewers/Response to Reviewers_00.tex

% An example for the ar2rc document class.
% Copyright (C) 2017 Martin Schroen
% Modifications Copyright (C) 2020 Kaishuo Zhang
%
% This program is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program.  If not, see <http://www.gnu.org/licenses/>.

% Use quote enviromnent for manuscript text

\documentclass{AR2RC}

\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{array}
\usepackage{multicol}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{float}
\usepackage[justification=centering]{caption}
\usepackage{tabularx}
\usepackage{booktabs}

\renewcommand{\arraystretch}{1.2}

\hypersetup{hidelinks}

\title{Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals}
\author{Mathieu Simon, Michael Indermaur, Denis Schenk, Seyedmahdi Hosseinitabatabaei, Bettina	M. Willie and Philippe Zysset}
\journal{Bone}
\doi{BONE-D-21-00758-R1}

\begin{document}

\maketitle

\vspace{1em}Once again, the authors would like to thank the reviewers for helping us to improve our article. We do believe that their and our time spent working on this document will definitively improve its message to the scientific community. As for the first revision, answers to comments are provided point by point in this document. In the revised manuscript, the added elements are written in blue and the canceled text is in red.

\section{Density}
\RC The first highlight states that OI trabecular bone is more mineralized compared to healthy bone, but the first sentence in the last paragraph of the Abstract says that OI bone is significantly less dense than healthy controls. This is going to be confusing for many. You need to clarify, which is presumably because you’re referring to tissue density in one case and apparent density in the other.

\AR Yes, you are right. To improve clarity the highlight and the abstract were modified as follow:

Highlight 1
\begin{quote}
	Osteogenesis Imperfecta (OI) \Del{trabecular} bone \Add{tissue} is more mineralized compared to healthy
\end{quote}

Abstract, last paragraph, first sentence
\begin{quote}
	In conclusion, OI trabecular bone of the distal tibia was shown to be significantly more heterogeneous and \Del{less dense} \Add{have a lower BV/TV} than healthy controls
\end{quote}

\section{Groups age ranges}
\RC Your response to the reviewer (2.9) incorrectly states the mean and plus/minus age of both groups (at least comparing to the comments in Methods 2.1). Which are the correct numbers?

\AR Effectively the numbers are different but both are correct. On one hand, in Methods 2.1 the mean and plus/minus age of both groups refers to the entire cohort. On the other hand, the response to reviewer 2.9 refers to Results 3.1 after the sex and age matching of groups. We forgot to precise it in the first response to reviewers.

\section{Typo}
\RC Page 3, second column, 4th line: Please fix typo “no enough” for “not enough”.

\AR This was changed.

\section{Exponential notation}
\RC Page 9, second column, 11th line from bottom: Why express the modulus as an exponent as such? Is this a typo? Currently it is written “10\textsuperscript{0}”. Why not write 1 MPa?

\AR This format was chosen because the text refers to Figure 5b (see below) where the exponential scale is written in power of 10. To improve clarity, the text was changed as shown here:

Page 9, second column, Discussion, Lines 50-52
\begin{quote}
	The linear regression plot (Figure 5b) shows that when the stiffness term decreases to \Add{1 MPa (}10\textsuperscript{0}\Add{)} \Del{MPa} and lower, the linear regression tends to overestimate the stiffness.
\end{quote}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]
	{Pictures/02_GR_OI_LMM}
	\caption{Linear regression results for original OI group using the fixed effects of the linear mixed-effect model.}
	\label{CV_BVTV2}
\end{figure}

\newpage
\section{Clinical refocusing}
\RC Both reviewers were concerned about the fit of the manuscript content with the audience of Bone. While I agree that the Bone audience is accustomed to technical papers, please consider further refocusing to the clinical aspect. I would question where it is necessary to explicitly include equations 2 and 3 (page 4) since those are presumably outlined in the cited reference. If needed at all, considering moving to Appendix. Furthermore, equation 7 is not explained and therefore its relevance (and frequent reference later in the Discussion) is not clear.

\AR We understand your concern and agree to further refocusing to the clinical aspect. Regarding equations 2 and 3, even if they are outlined in cited references, we think that they are necessary for technical completeness. On the other hand, as they are more related to technical aspect we moved them in Appendix, as suggested. The text citing equation 7 was modified to describe the term contained and the signification of this NE, see below. We hope that these firsts steps will help to decrease the technical difficulty and increase the clarity of the paper from a clinical point of view.

Page 5, second column, Methods 2.5.3, last paragraph
\begin{quote}
	\begin{equation}
	\text{NE} = \sqrt{\frac{(\mathbb{S}_o - \mathbb{S}_p) :: (\mathbb{S}_o - \mathbb{S}_p)}{\mathbb{S}_o :: \mathbb{S}_o}}
	\label{Eq206}
	\end{equation}

	\Add{Where $\mathbb{S}_o$ and $\mathbb{S}_p$ are the observed and predicted stiffness tensors, respectively. This relative norm error allows to quantify the accuracy of the prediction.}
\end{quote}

\section{Results validity}
\RC Most importantly, both reviewers had concerns about the validity of the results across the entire range of trabecular bone microarchitecture encountered in OI, and in particular the case where filtering was required to exclude highly heterogeneous bone microarchitecture. While it is understood that the focus of the paper is to explore whether fabric-elasticity relationships in OI and healthy bone are similar (thus justifying why filtering was performed), it is concluded that this is “encouraging the use of HR-pQCT based hFE outcomes for fracture risk assessment.” The comment about future fracture prediction by hFE is of course very important clinically, but the messaging about how to use these results are still not clear. Both the Abstract and the Discussion should comment on the implications of the fabric-elastic relationship not being defined for highly heterogeneous bone. Firstly, given there is only one OI type III where ROIs could be extracted, does this mean hFE should be restricted to OI type I? What evidence is there that it can be employed for OI type III or IV? This needs to be clearly justified. Second, in the future, when significant heterogeneity is encountered in a bone, do you still recommend to use hFE? In other words, please comment whether the findings of skewness for high heterogeneity affects if/when hFE is appropriate, and if there are alternatives to hFE in that case.

\AR Higly heterogeneous bone is rare in healthy conditions leading to the observed good correlations between simulations and experiments in the work of Varga et al. 2011, Hosseini et al. 2017, and Arias-Moreno et al. 2019. However, high heterogeneity arise from low bone volume fraction as outlined in the plot relating CV and BV/TV. This fact is determinant. As low BV/TV will lead to low stiffness, the error performed on such ROI is negligible as it not have a significant contribution to the stiffness of the full tibial section. For example, the observed stiffness component $\lambda_{ii}$ of one highly heterogeneous ROI (worst case) is around 1 MPa and the predicted value is around 100 MPa. This error is relatively small in comparison with the homogeneous ROI presenting a value around 10 GPa. Thus, only homogeneous ROIs (i.e. ROIs with higher BV/TV) contribute significantly to the bone stiffness. Moreover, despite the contribution of trabecular bone, the cortical bone will contribute even more significantly to tibial stiffness. Cortical bone having a higher BV/TV than trabecular bone, the relative error is low. Another point is that ROIs here have 5.3mm side length, reducing this size will improve homogeneity of ROIs and thus reduce error of the stiffness estimation. To improve the clarity of the message regarding validity of hFE among the OI types or heterogeneous bone, the manuscript was modified as follow:

Abstract, paragraph 4, last sentence
\begin{quote}
	The stiffnesses of highly heterogeneous ROIs were randomly lower with respect to the fabric-elasticity relationships, which reflects the limit of validity of the computational homogenisation methodology. \Add{Nevertheless, the error performed on these highly heterogeneous ROIs is negligible in comparison with homogeneous ROIs which are order of magnitude stiffer.}
\end{quote}

Discussion, Page 10, Second Column, Line 30
\begin{quote}
	\Add{Nevertheless, it should be noted that this relation between BV/TV and CV as well as the homogenization process (i.e. fabric-elasticity relationships) are independent of the OI type. Distribution of OI types for CV in relation to BV/TV as well as the linear regression of the original data set are available in Appendix D.}
\end{quote}

Discussion, Page 10, second column, last paragraph, last sentence
\begin{quote}
	Thus, the same hFE methodology can be applied for bone stiffness assessment of OI diagnosed individuals as for healthy ones\Add{, regardless the OI type}. Although in hFE analysis it is not possible to exclude part of the mesh because of high heterogeneity, the influence of such ROIs seems negligible on full bone models as the fabric-elasticity relationships can extrapolate their stiffness smoothly and as this concerns only ROIs with low BV/TV and stiffness.\Add{ Moreover, ROI side length can be reduced to improve accuracy if necessary for trabecular bone presenting extremely low BV/TV (and thus high heterogeneity), such as in OI tpye III.}
\end{quote}

\section{Supplementary material}
\RC It is suggested that Figure 2 in the response to reviewers be included in the manuscript (appendix or supplementary material).

\AR As required, the Figure was added in Appendix D

\end{document}

### 2021-11-18 09_Article/01_Revision2_Reviewers/Simon_2021_Bone_Manuscript_Revised.tex
Draft of second revision

		Compared to healthy controls, we found the OI samples to have significantly lower CV, BV/TV and trabecular number (Tb.N.), significantly higher trabecular separation (Tb.Sp.) and trabecular separation standard deviation (Tb.Sp.SD), but no differences in trabecular thickness (Tb.Th.). These results are in agreement with previous studies. The stiffnesses of highly heterogeneous ROIs were randomly lower with respect to the fabric-elasticity relationships, which reflects the limit of validity of the computational homogenisation methodology.

		The filtering of highly heterogeneous ROIs removed these low stiffness ROIs and led to similar correlation coefficients for both OI and healthy groups. Finally, the BV/TV and DA matched data revealed no significant differences in fabric-elasticity parameters between OI and healthy individuals. Compared to previous studies, the stiffness constants from the 61 \si{\micro}m resolution HR-pQCT ROIs were lower than for the 36 \si{\micro}m resolution \si{\micro}CT ROIs.

		In conclusion, OI trabecular bone of the distal tibia was shown to be significantly more heterogeneous and less dense than healthy controls. Despite the reduced linear regression parameters found for HR-pQCT images, the fabric-elasticity relationships between OI and healthy individuals are similar when the trabecular bone ROIs are sufficiently homogeneous to perform the computational stiffness analysis.  Accordingly, the elastic properties used for FEA of healthy bones are also valid for OI bones.
	\end{abstract}

@@

	In general, six cubic ROIs were selected at random position in each scan in a predefined area. Each ROI had to contain trabecular bone, but no cortical bone. For the healthy group, the ROIs were selected in the most proximal stack uniquely (see Figure \ref{01_Healthy} stack number 1) to be at roughly the same anatomical location as for the OI group. Then, for both the healthy group and the OI group, the stack was divided into two halves with a transverse plane and the ROIs were selected to have the centers of three ROIs in the proximal half and three in the distal half, see Figure \ref{01_ROISelection}. For one individual diagnosed with OI type III it was not possible to extract any ROI as there was no enough trabecular bone. This led to 720 healthy ROIs from 120 individuals and 294 OI ROIs from 49 individuals.\\

@@

	A \si{\micro}FE analysis was performed using \textsc{ABAQUS 6.14}. In brief, each voxel of the cleaned ROI was converted to a fully integrated linear brick elements (C3D8) using a direct voxel conversion approach. Then, a Young's modulus $E$ of 10,000 MPa and a Poisson's ratio $\nu$ of 0.3 were assigned to each element. The homogenisation process consisted of 6 independent simulations of different load cases, 3 uni-axial and 3 simple shear cases, using kinematic uniform boundary conditions (KUBCs) \cite{Panyasantisuk2015}. Unlike periodicity-compatible mixed uniform boundary conditions (PMUBCs), KUBCs do not require to rotate the ROI into the respective fabric coordinate system. Such rotation would potentially decrease image quality due to interpolation. The homogenization process allowed to calculate the components of the stiffness tensor and to calibrate the parameters of the Zysset-Curnier fabric-elasticity model \cite{Zysset1995}. This model computes the fourth order stiffness tensor $\mathbb{S}$ using the BV/TV or $\rho$, fabric tensor $\mathbf{M}$, three elasticity parameters $\lambda_0$, $\lambda_0$', and $\mu_0$, and two exponents, $k$ and $l$, as shown in Equation \ref{Eq202}.\\

	Where $\otimes$ and $\overline{\underline{\otimes}}$ are the dyadic and symmetric product of second order tensors, respectively. To express the stiffness tensor obtained from the homogenisation process with the Zysset-Curnier model, it had to be transformed into the fabric coordinate system using a coordinates transformation formula (see Equation \ref{Eq203p}) and projected onto orthotropy, leading to 12 components.

	Where $\mathbb{S}'$ and $\mathbb{S}$ are the transformed and the original stiffness tensor respectively and $\mathbf{Q}$ is the orthogonal matrix that maps the original coordinate system into the new one (fabric). The Zysset-Curnier model is built with the assumption of orthotropy and homogeneity of the ROI. However, the natural trabecular structure is not perfectly homogeneous. To assess the ROI heterogeneity, a coefficient of variation (CV) is computed according to \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015}: the ROI is divided into eight identical sub-cubes and BV/TV is computed for each of them. The CV is defined as the ratio between the standard deviation of these $\mathrm{BV/TV_i}$ and the mean value (Equation \ref{Eq203}).

@@

	The linear regression was performed using the \textsc{statsmodels} package from \textsc{Python 3.6}. Linear regression quality for the TMD analysis was assessed using the Pearson correlation coefficient squared ($R^2$) and the standard error of the estimate (SE). Linear regression on Zysset-Curnier model was assessed using the adjusted Pearson correlation coefficient squared ($R^2_{adj}$) and relative error between the orthotropic observed and the predicted tensor using norm of fourth-order tensors (NE), see Equation \ref{Eq205} and \ref{Eq206}.

@@

@@

	The linear regressions performed in this study on original data sets showed $R^2_{adj}$ and NE in the expected range (i. e. slightly lower than \citeauthor{Gross2013}\cite{Gross2013} and \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015}) for the healthy group. Components of the stiffness tensors are distributed to both sides of the diagonal. On the other hand, the linear regressions performed in this study using the original OI data set presents lower $R^2_{adj}$ and higher NE than comparable linear regressions in literature \cite{Gross2013,Panyasantisuk2015}. The important value of NE and its standard deviation shows that the fitted stiffness can deviate significantly from the observation. These differences come from ROIs presenting a low stiffness. The linear regression plot (Figure \ref{02_OI}) shows that when the stiffness term decreases to $10^0$ MPa and lower, the linear regression tends to overestimate the stiffness. This is because ROI stiffness is highly dependent on BV/TV values. Some ROIs with low BV/TV do not have every side of the cube connected by bone, leading to extremely low terms in the stiffness tensor (see Appendix \ref{A2}). Trying to homogenise such ROIs can lead to errors of multiple order of magnitude, as observed on the plot (Figure \ref{02_OI}). Therefore, a filtering is indispensable to assess and compare fabric-elasticity relationships, as done by \citeauthor{Panyasantisuk2015} \cite{Panyasantisuk2015}. An alternative to CV filtering for assessing the ROI heterogeneity could be to compute the proportion of the area filled by bone on each of the six faces of the ROI. \\

	Figure \ref{02_CV_BVTV} presents the CV in relation to BV/TV. It shows a tendency of CV values to increase with decreasing BV/TV values. Effectively, if the quantity of material inside the ROI decreases, the distribution homogeneity of this mass is more sensitive and therefore can quickly become highly heterogeneous. A simple assumption about this relation is that it could be monotonic. Pearson's correlation coefficient being strictly negative confirms a negative monotonic relation. As some ROIs with higher BV/TV still present high CV values, imposing a fixed threshold for subsequent homogenisation seems feasible. However, the value of this threshold results from an optimisation process in the study of \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015} and could be investigated further. \\

@@

	After BV/TV and DA matching, grouping the data sets together led to similar $R^2_{adj}$ and NE as for the individual filtered data sets. This allows one to determine values for $k$ and $l$ for the tibia at a spatial resolution of 61 \si{\micro}m. Imposing these values to perform the linear regression on data sets of the matched individuals allows us to highlight differences, if any, between healthy and OI trabecular bone. The relatively low differences for $\lambda_0'$ and $\mu_0$ once again supports the hypothesis for similar fabric-elasticity relationships between healthy and OI trabecular bone. For $\lambda_0$, this relative difference being higher could rise some doubts about this similarity, but the 95\% CI intervals still show a common range which almost include both the $\lambda_0$ of OI and healthy linear regressions. Moreover, ANCOVA performed comparing the original formulation and the one with addition of a regressor for the group showed a p-value far above the 5\% significance level. With this statistical non-significance of the groups and their low relative differences in the computed stiffness constants, it can be stated that: if trabecular bone is homogeneous enough, there is no reason to assume differences in fabric-elasticity relationships between healthy and OI trabecular bone. Thus, the same hFE methodology can be applied for bone stiffness assessment of OI diagnosed individuals as for healthy ones. Although in hFE analysis it is not possible to exclude part of the mesh because of high heterogeneity, the influence of such ROIs seems negligible on full bone models as the fabric-elasticity relationships can extrapolate their stiffness smoothly and as this concerns only ROIs with low BV/TV and stiffness.\\

@@

	%\clearpage
	\appendix
	\section{Linear Models}\label{A1}

@@

	\clearpage
	% Loading bibliography database
	\bibliographystyle{BibStyle}
	\bibliography{Bibliography}

>>>>

		Compared to healthy controls, we found the OI samples to have significantly lower BV/TV and trabecular number (Tb.N.), significantly higher CV, trabecular separation (Tb.Sp.) and trabecular separation standard deviation (Tb.Sp.SD), but no differences in trabecular thickness (Tb.Th.). These results are in agreement with previous studies. The stiffnesses of highly heterogeneous ROIs were randomly lower with respect to the fabric-elasticity relationships, which reflects the limit of validity of the computational homogenisation methodology. \Add{Nevertheless, the error performed on these highly heterogeneous ROIs is negligible in comparison with homogeneous ROIs which are order of magnitude stiffer.}

		The filtering of highly heterogeneous ROIs removed these low stiffness ROIs and led to similar correlation coefficients for both OI and healthy groups. Finally, the BV/TV and DA matched data revealed no significant differences in fabric-elasticity parameters between OI and healthy individuals.\Add{ Moreover, the filtering step did not exclude a particular OI type.} Compared to previous studies, the stiffness constants from the 61 \si{\micro}m resolution HR-pQCT ROIs were lower than for the 36 \si{\micro}m resolution \si{\micro}CT ROIs.

		In conclusion, OI trabecular bone of the distal tibia was shown to be significantly more heterogeneous and \Del{less dense} \Add{have a lower BV/TV} than healthy controls. Despite the reduced linear regression parameters found for HR-pQCT images, the fabric-elasticity relationships between OI and healthy individuals are similar when the trabecular bone ROIs are sufficiently homogeneous to perform the computational stiffness analysis.  Accordingly, the elastic properties used for FEA of healthy bones are also valid for OI bones.
	\end{abstract}

@@

	In general, six cubic ROIs were selected at random position in each scan in a predefined area. Each ROI had to contain trabecular bone, but no cortical bone. For the healthy group, the ROIs were selected in the most proximal stack uniquely (see Figure \ref{01_Healthy} stack number 1) to be at roughly the same anatomical location as for the OI group. Then, for both the healthy group and the OI group, the stack was divided into two halves with a transverse plane and the ROIs were selected to have the centers of three ROIs in the proximal half and three in the distal half, see Figure \ref{01_ROISelection}. For one individual diagnosed with OI type III it was not possible to extract any ROI as there was no\Add{t} enough trabecular bone. This led to 720 healthy ROIs from 120 individuals and 294 OI ROIs from 49 individuals.\\

@@

	A \si{\micro}FE analysis was performed using \textsc{ABAQUS 6.14}. In brief, each voxel of the cleaned ROI was converted to a fully integrated linear brick elements (C3D8) using a direct voxel conversion approach. Then, a Young's modulus $E$ of 10,000 MPa and a Poisson's ratio $\nu$ of 0.3 were assigned to each element. The homogenisation process consisted of 6 independent simulations of different load cases, 3 uni-axial and 3 simple shear cases, using kinematic uniform boundary conditions (KUBCs) \cite{Panyasantisuk2015}. Unlike periodicity-compatible mixed uniform boundary conditions (PMUBCs), KUBCs do not require to rotate the ROI into the respective fabric coordinate system. Such rotation would potentially decrease image quality due to interpolation. The homogenization process allowed to calculate the components of the stiffness tensor and to calibrate the parameters of the Zysset-Curnier fabric-elasticity model \cite{Zysset1995}. This model computes the fourth order stiffness tensor $\mathbb{S}$ using the BV/TV \Del{or $\rho$}, fabric tensor $\mathbf{M}$, three elasticity parameters $\lambda_0$, $\lambda_0$', and $\mu_0$, and two exponents, $k$ and $l$\Del{, as shown in Equation \ref{Eq202}}. \Add{This stiffness tensor is then transformed into the fabric coordinate system} and projected onto orthotropy, leading to 12 components. \Add{The technical details of the computations performed are presented in Appendix \ref{A0}.}\\

	The Zysset-Curnier model is built with the assumption of orthotropy and homogeneity of the ROI. However, the natural trabecular structure is not perfectly homogeneous. To assess the ROI heterogeneity, a coefficient of variation (CV) is computed according to \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015}: the ROI is divided into eight identical sub-cubes and BV/TV is computed for each of them. The CV is defined as the ratio between the standard deviation of these $\mathrm{BV/TV_i}$ and the mean value (Equation \ref{Eq203}).

@@

	The linear regression was performed using the \textsc{statsmodels} package from \textsc{Python 3.6}. Linear regression quality for the TMD analysis was assessed using the Pearson correlation coefficient squared ($R^2$) and the standard error of the estimate (SE). Linear regression on Zysset-Curnier model was assessed using the adjusted Pearson correlation coefficient squared ($R^2_{adj}$) and relative error between the orthotropic observed and the predicted tensor using norm of fourth-order tensors (NE), see Equation \ref{Eq205} and \ref{Eq206}\Add{, respectively}.

@@

	\Add{Where $\mathbb{S}_o$ and $\mathbb{S}_p$ are the observed and predicted stiffness tensors, respectively. This relative norm error allows to quantify the accuracy of the prediction.}

@@

	The linear regressions performed in this study on original data sets showed $R^2_{adj}$ and NE in the expected range (i. e. slightly lower than \citeauthor{Gross2013}\cite{Gross2013} and \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015}) for the healthy group. Components of the stiffness tensors are distributed to both sides of the diagonal. On the other hand, the linear regressions performed in this study using the original OI data set presents lower $R^2_{adj}$ and higher NE than comparable linear regressions in literature \cite{Gross2013,Panyasantisuk2015}. The important value of NE and its standard deviation shows that the fitted stiffness can deviate significantly from the observation. These differences come from ROIs presenting a low stiffness. The linear regression plot (Figure \ref{02_OI}) shows that when the stiffness term decreases to \Add{1 MPa (}10\textsuperscript{0}\Add{)} \Del{MPa} and lower, the linear regression tends to overestimate the stiffness. This is because ROI stiffness is highly dependent on BV/TV values. Some ROIs with low BV/TV do not have every side of the cube connected by bone, leading to extremely low terms in the stiffness tensor (see Appendix \ref{A2}). Trying to homogenise such ROIs can lead to errors of multiple order of magnitude, as observed on the plot (Figure \ref{02_OI}). Therefore, a filtering is indispensable to assess and compare fabric-elasticity relationships, as done by \citeauthor{Panyasantisuk2015} \cite{Panyasantisuk2015}. An alternative to CV filtering for assessing the ROI heterogeneity could be to compute the proportion of the area filled by bone on each of the six faces of the ROI. \\

	Figure \ref{02_CV_BVTV} presents the CV in relation to BV/TV. It shows a tendency of CV values to increase with decreasing BV/TV values. Effectively, if the quantity of material inside the ROI decreases, the distribution homogeneity of this mass is more sensitive and therefore can quickly become highly heterogeneous. A simple assumption about this relation is that it could be monotonic. Pearson's correlation coefficient being strictly negative confirms a negative monotonic relation. As some ROIs with higher BV/TV still present high CV values, imposing a fixed threshold for subsequent homogenisation seems feasible. However, the value of this threshold results from an optimisation process in the study of \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015} and could be investigated further. \Add{Nevertheless, it should be noted that this relation between BV/TV and CV as well as the homogenization process (i.e. fabric-elasticity relationships) are independent of the OI type. Distribution of OI types for CV in relation to BV/TV as well as the linear regression of the original data set are available in Appendix} \ref{A3}\Add{.} \\

@@

	After BV/TV and DA matching, grouping the data sets together led to similar $R^2_{adj}$ and NE as for the individual filtered data sets. This allows one to determine values for $k$ and $l$ for the tibia at a spatial resolution of 61 \si{\micro}m. Imposing these values to perform the linear regression on data sets of the matched individuals allows us to highlight differences, if any, between healthy and OI trabecular bone. The relatively low differences for $\lambda_0'$ and $\mu_0$ once again supports the hypothesis for similar fabric-elasticity relationships between healthy and OI trabecular bone. For $\lambda_0$, this relative difference being higher could rise some doubts about this similarity, but the 95\% CI intervals still show a common range which almost include both the $\lambda_0$ of OI and healthy linear regressions. Moreover, ANCOVA performed comparing the original formulation and the one with addition of a regressor for the group showed a p-value far above the 5\% significance level. With this statistical non-significance of the groups and their low relative differences in the computed stiffness constants, it can be stated that: if trabecular bone is homogeneous enough, there is no reason to assume differences in fabric-elasticity relationships between healthy and OI trabecular bone. Thus, the same hFE methodology can be applied for bone stiffness assessment of OI diagnosed individuals as for healthy ones\Add{, regardless the OI type}. Although in hFE analysis it is not possible to exclude part of the mesh because of high heterogeneity, the influence of such ROIs seems negligible on full bone models as the fabric-elasticity relationships can extrapolate their stiffness smoothly and as this concerns only ROIs with low BV/TV and stiffness.\Add{ Moreover, ROI side length can be reduced to improve accuracy if necessary for trabecular bone presenting extremely low BV/TV (and thus high heterogeneity).}\\

@@

	%\clearpage
	\appendix
	\section{Technical Computations}\label{A0}

	The Zysset-Curnier model \cite{Zysset1995} computes the fourth order stiffness tensor $\mathbb{S}$ using the BV/TV or $\rho$, fabric tensor $\mathbf{M}$, three elasticity parameters $\lambda_0$, $\lambda_0$', and $\mu_0$, and two exponents, $k$ and $l$, as shown in Equation \ref{Eq202}.

	Where $\otimes$ and $\overline{\underline{\otimes}}$ are the dyadic and symmetric product of second order tensors, respectively. To express the stiffness tensor obtained from the homogenisation process with the Zysset-Curnier model, it had to be transformed into the fabric coordinate system using a coordinates transformation formula, see Equation \ref{Eq203p}.

	Where $\mathbb{S}'$ and $\mathbb{S}$ are the transformed and the original stiffness tensor respectively and $\mathbf{Q}$ is the orthogonal matrix that maps the original coordinate system into the new one (fabric). After transformation, the stiffness tensor is projected onto orthotropy, leading to 12 components which can be represented in a 6x6 matrix as follow:

	\begin{equation}
	\mathbb{S} = 
	\begin{pmatrix}
		\lambda_{11} & \lambda_{12} & \lambda_{13} & 0 & 0 & 0 \\
		\lambda_{21} & \lambda_{22} & \lambda_{23} & 0 & 0 & 0 \\
		\lambda_{31} & \lambda_{32} & \lambda_{33} & 0 & 0 & 0 \\
		0 & 0 & 0 & \mu_{23} & 0 & 0 \\
		0 & 0 & 0 & 0 & \mu_{31} & 0 \\
		0 & 0 & 0 & 0 & 0 & \mu_{12}
	\end{pmatrix}
	\label{Eq203x}
	\end{equation}

	\section{Linear Models}\label{A1}

@@

	\clearpage
	\section{OI Types Properties Distribution}\label{A3}

	As the OI cohort is composed of different OI types, it was verified that the analyses performed where not sensitive to the type of OI.

	\begin{figure}[h]
		\centering
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]
			{Pictures/R2_CV_BVTV}
			\caption{CV in relation to BV/TV.}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]
			{Pictures/R2_LinearRegression}
			\caption{Linear regression of the complete OI data set.}
		\end{subfigure}
		\hspace{-5mm}\caption{Relative positions of the different OI types for different analyses.}
	\end{figure}

	%\clearpage
	% Loading bibliography database
	\bibliographystyle{BibStyle}
	\bibliography{Bibliography}
